Unit tests

### 2018-03-08 Tests.Rmd
trivial

Test for unbiased estimator of third central moment:
```{r test_myskewness, echo=F, cache=T, cache.extra=list(mtime("SkewnessAnd3CentMom.R"))}
source("SkewnessAnd3CentMom.R")
set.seed(101)

>>>>

Test for unbiased estimator of third central moment:
```{r test_myskewness, echo=T, cache=T, cache.extra=list(mtime("SkewnessAnd3CentMom.R"))}
source("SkewnessAnd3CentMom.R")
set.seed(101)
